Type Refinements for the Working Class

### 2016-01-03 paper.tex
make modalities a section rather than a subsection
add "structural"
fix typos

There are two conflicting views which bedevil any discussion of the nature of
type theory. First, there is the notion of type theory as an extension or
generalization of universal algebra to support interdependency of sorts and
operations, possibly subject to an arbitrary equational theory
\cite{cartmell:1986, dybjer:1996}; we will call this \emph{formal type theory}.
Typing, in such a setting, is a mere matter of grammar and is nearly always
decidable. In hindsight, we may observe that this is the sort of type theory
which Martin-L\"of first proposed in 1972~\cite{martin-lof:1972}, even if we
will admit that this was not the intention at the time. A model for such a type
theory is usually given by interpreting the types or sorts as presheaves or
sheaves over contexts of hypotheses, and as such, a proof theoretic
interpretation of the hypothetical judgment is possible.

@@

The set comprehension $\MkSet{x:\phi\mid\psi}$ contains just those elements of
$\phi$ such that their fibers of $\psi$ are inhabited; this can be seen as an
``implicit'' version of existential quantification, and can be used to
simultaneously specify and implement program without the evidence for $\psi$
intruding into the extracted algorithm.

@@

    \item
      For any
      \begin{tikzcd}[cramped]
        \IMode{\Upsilon'} \arrow[r,hook,"\IMode{\rho'}"] &\IMode{\Upsilon''}
      \end{tikzcd}%
      , for all $\Member{\sigma}{\Sorts}$ and $\Member{X,X',Y}{\Exprs_\sigma(\Upsilon'')}$, if
      from $\EvalN{\Upsilon''}{\sigma}{k'}{X}{X'}$ for $\IMode{k'}<\IMode{k}$ and
      $\PBinRel{\preccurlyeq^\star_\sigma}{\Upsilon''}{X}{Y}$, we can conclude
      $\PBinRel{\preccurlyeq^\star_\sigma}{\Upsilon''}{X'}{Y}$.
  \end{enumerate}

@@

\subsection{Refinement Modalities}

@@

\subsubsection{Nominal Independence}

@@

\subsubsection{Nominal Necessity}

@@

\subsubsection{Nominal Possibility}

>>>>

There are two conflicting views which bedevil any discussion of the nature of
type theory. First, there is the notion of type theory as an extension or
generalization of universal algebra to support interdependency of sorts and
operations, possibly subject to an arbitrary equational theory
\cite{cartmell:1986, dybjer:1996}; we will call this \emph{formal} or
\emph{structural type theory}.  Typing, in such a setting, is a mere matter of
grammar and is nearly always decidable. In hindsight, we may observe that this
is the sort of type theory which Martin-L\"of first proposed in
1972~\cite{martin-lof:1972}, even if we will admit that this was not the
intention at the time. A model for such a type theory is usually given by
interpreting the types or sorts as presheaves or sheaves over contexts of
hypotheses, and as such, a proof theoretic interpretation of the hypothetical
judgment is possible.

@@

The set comprehension $\MkSet{x:\phi\mid\psi}$ contains just those elements of
$\phi$ such that their fibers of $\psi$ are inhabited; this can be seen as an
``implicit'' version of existential quantification, and can be used to
simultaneously specify and implement programs without the evidence for $\psi$
intruding into the extracted algorithm.

@@

    \item
      For any
      \begin{tikzcd}[cramped]
        \IMode{\Upsilon'} \arrow[r,hook,"\IMode{\rho'}"] &\IMode{\Upsilon''}
      \end{tikzcd}%
      , for all $\Member{\sigma}{\Sorts}$ and $\Member{X,X',Y}{\Exprs_\sigma(\Upsilon'')}$,
      from $\EvalN{\Upsilon''}{\sigma}{k'}{X}{X'}$ for $\IMode{k'}<\IMode{k}$ and
      $\PBinRel{\preccurlyeq^\star_\sigma}{\Upsilon''}{X}{Y}$, we can conclude
      $\PBinRel{\preccurlyeq^\star_\sigma}{\Upsilon''}{X'}{Y}$.
  \end{enumerate}

@@

\section{Refinement Modalities}

@@

\subsection{Nominal Independence}

@@

\subsection{Nominal Necessity}

@@

\subsection{Nominal Possibility}
